Project Report\\\textsc{DEVS Ex Machina}

### 2015-04-25 manual/projectrapport.tex
project report, added design uml, NEEDS TO BE VERIFIED
Addition of short Documentation section to manual

\title{Project Rapport\\\textsc{DEVS Ex Machina}}
\author{Ben Cardoen\\Pieter Lauwers\\Stijn Manhaeve\\Tim Tuijn\\Matthijs Van Os}
\date{}
\begin{document}
\maketitle
\tableofcontents{}

@@

\chapter{Design}
\section{Overview}
We've slightly departed from the PyPDEVS structure, to allow for more encapsulation and decoupling of the core entities. This clear separation of data and responsibilities between classes made the threading part of the 
project easier (no or minimal shared state).
%TODO include UML overview

@@

\section{Models}
The models hide all implementation details for the particular DEVS formalisms, without limiting the user to extend into any subclassed model of his/her choice. The use can focus on what he/she wants the model to emulate, and not worry about for example locking, allocation etc. We refer to the manual for more information about the creation of these models.

@@

\section{Controller}
%TODO Matthijs

>>>>

\title{Project Report\\\textsc{DEVS Ex Machina}}
\author{Ben Cardoen\\Pieter Lauwers\\Stijn Manhaeve\\Tim Tuijn\\Matthijs Van Os}
\date{}
\begin{document}
\maketitle
\tableofcontents{}

@@

\chapter{Design}
\section{Overview}
We've slightly departed from the PyPDEVS structure, to allow for more encapsulation and decoupling of the core entities. This clear separation of data and responsibilities between classes made the threading part of the project easier (no or minimal shared state). See the \hyperref[simpledesign]{Simple Design figure \ref*{simpledesign}}.\\

\begin{figure}[h!]
	\makebox[\textwidth][c]{\includegraphics[width=1.5\textwidth]{Design.png}}
	\caption{Simple Design}
	\label{simpledesign}
\end{figure}

@@

\section{Models}
The models hide all implementation details for the particular DEVS formalisms, without limiting the user to extend into any subclassed model of his/her choice. The user can focus on what he/she wants the model to emulate, and not worry about for example locking, allocation etc. We refer to the manual for more information about the creation of these models.

@@

\section{Controller}
For the controller, care was taken in making the interface both functional and minimal. The default configuration is quick to set up, and customization is possible should the user require it.
